\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-15 Supplymentary.Rmd
Figure captions in sup.analysis are updated

```{r figCorAppB,  fig.cap="Correlation plot of the items",  out.width="100%"}

@@

```{r facIdFigAppB,  fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

efa.table <- tabledown::fac.tab(fa.5F.4,.3)

@@

```{r EFATableAppB, results='asis'}

apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

>>>>

```{r figCorAppB,  fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}

@@

```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot' [Unmerged response options], warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F)

@@

```{r EFATableAppB, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

### 2021-11-15 manuscript.Rmd
Figure captions in sup.analysis are updated

  ) %>% 
  tab_row_group(
  group = "EFA (n = 428)",
    rows = 1:25  
  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 3000)

@@

```{r gtPic, echo=FALSE, out.height="100%", out.width="120%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
knitr::include_graphics('Manuscript.figures/gt.png')

>>>>

  ) %>% 
  tab_row_group(
  group = "EFA (n = 428)",
    rows = 1:25  
  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 7000)

@@

```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
knitr::include_graphics('Manuscript.figures/gt.png')

### 2021-11-15 manuscript.tex
Updated Flowchart1
Figure captions in sup.analysis are updated

{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{Manuscript.figures/Flowchart1}

@@

\begin{figure}
\includegraphics[width=1.2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
\end{figure}

@@

To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the ``Semantic Scale Network''(SSN) analysis(Rosenbusch et al., 2020). The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 (Rosenbusch et al., 2020). Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA appeared most strongly related to scales about sleep: ``Sleep Disturbance Scale For Children'' (Bruni et al., 1996) and ``WHO-Composite International Diagnostic Interview (CIDI): Insomnia''(WHO, 1990).The cosine similarities lie between .47 to .51. Two factors of our LEBA tool: ``Using phone and smart-watch in bed'' and ``Using light before bedtime'' dealt with light exposure related behavior pertaining to sleep quality. As such the similarity index obtained is expected.

@@

Table \ref{tab:itemfittab} summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation. All of the items had RMSEA value \textless.06 indicating adequate fit. Figure \ref{fig:personfit} depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

@@

Next, we generated scale characteristics curve (Figure \ref{fig:scalechar}) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:scalechar}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth,height=1.6\textheight]{Manuscript.figures/Flowchart1}

@@

\begin{figure}
\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
\end{figure}

@@

To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the ``Semantic Scale Network''(SSN) analysis (Rosenbusch et al., 2020). The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 (Rosenbusch et al., 2020). Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA appeared most strongly related to scales about sleep: ``Sleep Disturbance Scale For Children'' (Bruni et al., 1996) and ``WHO-Composite International Diagnostic Interview (CIDI): Insomnia''(WHO, 1990).The cosine similarities lie between .47 to .51. Two factors of our LEBA tool: ``Using phone and smart-watch in bed'' and ``Using light before bedtime'' dealt with light exposure related behavior pertaining to sleep quality. As such the similarity index obtained is expected.

@@

Table \ref{tab:itemfittab} summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation. All of the items had RMSEA value \(\le\).06 indicating adequate fit. Figure \ref{fig:personfit} depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

@@
